Transforming Trash as an Artistic Act

### 2016-01-17 chapter1_final.tex
Proof reading
Former-commit-id: d835c4ff57c702c8f90dae1816f3609db8679019

%
%
%\summary{Trash exists in every age and every society} 
Refuse is part of people's daily consumption practices. It is a very common concept from developed cities to rural areas, from modern societies to ancient ones \citep[33]{rathje1992rubbish}. 
%\todo{more ref.} 
For archaeologist dumps are one of the significant places to figure out what people consume in the ancient times \citep{rathje1992rubbish}.
%\summary{Global}
%It is not limited with geography, ethnicity, gender, nationality. The process of retrieving and transforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban America as well as the remotest corners of the world.
Trash is everywhere and, produced every time. \quotes{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes} \citep{zimring2012encyclopedia}. Various activities of our life such as eating, drinking, working, traveling leave behind wastes. People are surrounded by all kinds of goods and they are consuming everywhere while walking, working and traveling. The pattern is spread to all day and different places. It is hard to say that any place is waste free. Nearly every place people require waste bin. If people do not find a waste bin, they often leave their trash to the ground. Production of trash never stops. It is inseparable from people's activities.
%\summary{Trash is everywhere} 
Trash is in the streets, in your home, in the sea that you swim, rotating around the globe \footnote{Satellite discards are disposed to the atmosphere and they rotate around the globe like satellites.}. Even if trash is tried to be moved away from people life, it is as close as nearest waste bin.

%
% FROM Trash as Treasure BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
%\summary{Facts}
\begin{quote}
The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization of 34 countries. Turkey is a member of this organization.} countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment \citep{fash2015trash}.
\end{quote}

% Üstteki kısmı neden diyorsun? Teze nasıl bir katkı sağlıyor? Throw away culture a taşınabilir.
% From recycled book.
Similar to these as stated by \cite{cerny1996recycled} \quotes{a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.}

%
%
%\summary{Moves} 
The vast amount of discarded items spread through the landfills to oceans. As commodities spread to the every corner of the world, trash do also. It moves from homes to garbage trucks, from streets to landfills and also from waste bins to sculptures. Various people including garbage collectors and artist touches to trash. It is not static, not fixed, not totally isolated from us.

@@

%\comment{What happens when it is traveled to the other countries, how do people approach these items? They find new uses and meanings on them because their understanding of that items is different.} \todo{Bu soru daha sonraki bölümde sorulabilir.}

%
%
%\summary{Common}
In the dictionary, 
%\todo{Which dictionary?}
trash means anything useless, worthless or discarded. In parallel to this definition, the common perception is to get rid of them as soon as possible. People tend to think that trash is valueless because it is no longer needed or not wanted anymore. People want to get rid of them not thinking any alternative. \quotes{They forget about it and don’t think about all the time and energy and money put into disposing of it} \citep{navarro2015followingtrash}. However to establish a solid understanding of trash and the action of trashing, we have to give attention to the trash. To move the beyond common perception we have to ask is it possible to do something other than refusing them? %\comment{Instead of creating new usages, combinations or alternatives, common approach is to ignore all the possibilities embedded to the trash. People do not see beyond the primary function.}

%
%
%\summary{Aspects and Approaches}
In this thesis study to understand the different aspects of trash is a key element. Sometimes it is accepted as a problem (because of accepted as dirty, smelly) that needs to be carefully and seriously managed. On the other hand it is accepted as a source of diversity by the artists. For the recyclers it is a source of income. The economical aspect of trash can not ignored. There are people who collects plastics, scraps and papers from waste bins and landfills. By collecting and selling them they endure their life.

As it can be seen clearly there are different aspects and approaches to the trash. For some people, it is disgusting thing and moved away from living space and for the others source (or treasure) of their life. It is noted that \quotes{perceptions of waste and the value of material are neither static nor universally shared} \citep{zimring2012encyclopedia}.

%\summary{Relative}
As stated by the editor of Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \citep{erlick2015editorsletter}. She realized that any of them called the practice as recycling. For them using trash again and again is very natural and it is part of their life. On the contrary for the developed countries trash considered as a thing that must be avoided. There is no place for trash in their life. It can be understood from this anectode that approaches to the garbage are not same for all regions of the world.

%
%
%\summary{Parts of us}
\begin{quote}
Our trash is a testament; what we throw away says much about our values, our habits, and our lives. ... Our trash is part of us, whether or not we choose to acknowledge it. ... The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream. \citep{zimring2012encyclopedia}
\end{quote}

% TODO Summarize
% FROM Book: Trash Culture
%\summary{Change in the production and consumption practices}
\quotes{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption. Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line} \citep{pye2010trashculture}. As the result of it amount of goods boost and the cost of them significantly reduced. Things once reused again and again, now thrown away because it is more affordable to replace with new one. As the production increased its by-product material waste is also increased. \quotes{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption} \citep{pye2010trashculture}.
%\todo{summarize}

%
%
%\summary{Current} 
During the last decades much attention has been devoted to the waste. In particularly environmental considerations dominates the perceptions of waste. \cite{ibarra2015beautiful} writes that \quotes{despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding}.

%
%
%\summary{Art}
As noted by \cite{pye2010trashculture} \quotes{at least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art}. Using non art objects in the art opened new dimensions for the language of art and practice (act) of art. In the beginning of the 20th century non-art objects 
%\todo{non-art objecti aç} 
enter the scope of art making. This is a revolutionary change in the practice of art making. Production of art and the approach to the art changed dramatically. 
%This changes actually started at the end of the 19th century with impressionist. 
Picasso is the first artist that used non-art object in his works. Later many of artists such as Kurt Schwitters and Joseph Cornell  followed him with their collages and assemblages. Later Duchamp challenged the nature (or language) of art by using, non-unique, fabricated object to express his ideas. His work changed the way of perceiving art dramatically. With these developments trash has found a place in the art and contemporary artists become interested in trash. They use trash for different purposes (and these are explored in detail in the following chapters.). Trash find places in many mediums such as sculptures, paintings, assemblages and photographs. Artist express themselves through trash. Portraits build from trash. Consumption habits of society are criticized through trash.

%
%****************************************
\section{Purpose of the Study}

% Bu tezde sorulan sorulardan birisi Çöpe daha farklı nasıl yaklaşılabilir... sanatçılardan örnekler verilerek bu açıklanmıştır.

% Some of the artist also interested in others trash. Why people are interested in rubbish?

% In this thesis (re-)usage of discarded materials in the process of art making and the artwork itself is explored.

The aim of this study is to explore the theories and methods of transformation of trash in the context of art and artistic act. 
% FROM Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
\quotes{Particularly in the connection between trash and the arts, this thesis is interested in two issues. First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as artistic material} \citep{ibarra2015beautiful}.
Why and how is trash used by the artist? Are there any differences with the original (or untouched, or blank) items compared to discarded (or used) items? Has using discarded material or trash have specific (or special) meaning and message? Questioned that how do artists reflect trash and what are their tactics?

%\paraphrase{Trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature \citep{pye2010trashculture}.}

% \paraphrase{This thesis seeks to answer the following questions: How did art and literature respond to this age of consumption? What do the productions and practices of artists and writers reveal about the meaning of mass production, consumption, reification (depersonalization), mechanical reproduction, and meaning? (FROM Collage Culture)}

%Do people want to take back (or revisit) the trash once thrown away
In my project, the purpose is to transform trash and make it worth to reconsider.

%
%
%\summary{Different types of trash, narrowing down scope} 
There are different types of trashes result of different production and consumption practices. For example radioactive waste is usually a by-product of nuclear power generation and other applications of nuclear fission or nuclear technology. Electronic waste (e-waste), construction and demolition waste, medical waste are some of them. As it can be seen that there are lots of different types and as various as activities of human. In this scope of thesis focused on disposable items and specifically paper trash.

%
%
%\summary{Different disciplines of trash, narrowing down scope}
Trash attract the attention of different peoples and disciplines \quotes{ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture} \citep{emgin2012trashion}. Technological perspectives are one of them. Trash is seen as a design and technological problem \citep{mcdonough2010cradle}.  
% Developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed? Developed in what sense? What are the criterion (foundation, measure) of technology? Technology is interested in which problems?)

% Management of it (handled by the municipals generally). Removal from the life spaces of human.

% FROM Recycled, Re-Seen: Folk Art from the Global Scrap Heap
In addition to these
\begin{quote}
%\vspace{-\baselineskip}
the process of [transformation] is not to be confused with the kind of industrial recycling to which we in the West are most accustomed. When we think of recycling in industrialized nations we imagine an automated sequence beginning with the curbside disposal of aluminum cans, plastic bottles, and old newspapers with the aim of returning them to the industrial process \citep{cerny1996recycled}. 
%\vspace{-\baselineskip}
\end{quote}

% TODO Relocate and contextualize
% Solid waste management, global greening, and ecological awareness are the buzzwords that guide and motivate consumers and industries to engage in this process of secondary and post consumer waste recycling.

Many people are inside the business of transforming trash through recycling and reusing. People on the streets looking for aluminum cans, glass bottles, plastic. They collect and sell them to survive. There are companies that are collect waste materials to regain them to the industry. In thesis they are not in the scope. Artist that give attention to the trash and transform them is in the scope of this thesis.

% TODO Relocate, summarize and contextualize
%\summary{Waste and technology relationship} 
%\paraphrase{We live in a badly engineered world, because the vast amounts of waste (both material and energetic) are needless; and that waste could be virtually eliminated through better design \citep{mcdonough2010cradle}.} \todo{can be moved to zizek part.} In other words, the problem is our technology (or design, or both) which is not perfect and causes mountains of rubbish. It is questionable that at some point, technology will reach to a level when there is no trash generated.

% TODO Relocate, summarize and contextualize
%\comment{Technical problem, need to managed, recycling (capitalism), upcycling} 
%\paraphrase{With respect to the issue of disposability, waste was handled merely “as a technical problem, something to be administered by the most efficient and rational technologies of removal.” Only through the rise of environmental movements in the 1960s did the disposal of waste come to be loaded with negative meanings and iewed through a moral framework. The enormous quantities of waste accumulating in urban centers, Hawkins writes in “Plastic Bags,” were not only taken as a threat to the environment, but also as a sign of an individualistic, insensitive, and hedonistic consumer society. Waste now became evil. If the environment is to be saved from our destructive power, then waste should be “managed,” Hawkins asserts. Consequently, recycling gained its contemporary prominence “as virtue-added disposal\ldots disposal in which the self is morally purified, disposal as an act of redemption.” Disposal in the form of recycling is now a moralistic attitude through which we pay the debt we owe to the world. Upcycling... On the other side of the coin is the business stemming from these practices; recyclers not only ease their conscience through recycling; they also make a profit. Recycling, as “the huge tertiary sector devoted to getting rid of things, is central to the maintenance of capitalism; it doesn’t just allow economies to function by removing excess and waste—it is an economy, realizing commercial value in what’s discarded,” Hawkins and Muecke write in Culture and Waste. In the same manner, upcycling has already been turned into a business: Certain designers labeled eco-friendly are earning money through upcycling, competitions are organized around trashion, numerous websites are devoted to promoting and selling upcycled objects, and online and print resources explain how to upcycle at home. In short, there is a whole sector of upcycling now.} \todo{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}

% TODO relocation.
% MOVE TO Conclusion of art chapter, discussion of transformation.
%\comment{Design, alternative discipline} \paraphrase{Design, as a conduit of disposal, reintroduces rubbish as objects of distinction, invaluable and potentially priceless. People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.} \todo[inline]{reference, (Trashion: The Return of the Disposed by Bahar Emgin)}

@@

%
%****************************************
\section{A Note on Terminology}
Many scholars and authors have used different words (or terminology) to define trash. Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter are some of them. Although there are slight differences between these words, sometimes they are used to signify same concept (or used with the same purposes). It signifies that the topic is so broad and there is no consensus on terminology. Words are used interchangeably. The book \quotes{Rubbish: the Archeology of Garbage} gives clearer definition of some these words:

%\comment{What were people throwing out when these words were coined?}

% FROM Rubbish! The Archaeology of Garbage, p.9, rathje1992rubbish
\begin{quote}
Several words for the things we throw away---"garbage", "trash", "refuse", "rubbish"--- are used synonymously in causal speech but in fact have different meanings. \textit{Trash} refers specifically to discards that are at least theoretically "dry"---newspapers, boxes, cans, and so on. \textit{Garbage} refers technically to wet discards--- food remains, yard waste, and offal. Refuse is an inclusive term for both the wet discards and the dry. Rubbish is even more inclusive: It refers to all refuse plus construction and demolition debris. The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrelevant, but may see a revival if the idea of composting food and yard waste catches on. We will frequently use "garbage" in this book to refer to the totality of human discards because it is the word used naturally in ordinary speech. The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen. \citep[9]{rathje1992rubbish}
\end{quote}

%From another book (Trash Culture):
%\paraphrase{Literature of trash feature a broad range of terms, reflecting the multifaceted and conceptually complex nature of the issue at hand. Many of these terms --- such as ‘trash’, ‘garbage’ and ‘rubbish’ --- are frequently used interchangeably. This is not least because the variety of terms reflects the variations in English and US vocabulary and thus all usages are retained as individual authors intended in order to reflect the international nature of this volume. Other related terms, such as ‘ruins’, ‘obsolete’, ‘waste’, ‘discards’ are used in a variety of contexts in each chapter.}

In addition to these there is also confusion of the terms: reuse and recycling which are the (general) methods of transforming trash to the another object. Both of them are used widely by scholars.

According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form. Reusing lengthens the life of the item or material. The main purpose is to make the item last as long as it can. To reuse is to use something again instead of throwing it away.

%Why throw something away when you can give it another life? Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose. In this thesis, it is explored through the work of the artist.

% Reusing is possible with re-seeing (and re-thinking). Using creativity and personal approach can change objects functions. It is possible to use objects for different purposes.

% TODO Summarize
According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product. For example, if we put some plastic bottles, paper, or aluminum items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt. Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product. Examples are crushed glass containers used to make new glass containers, and scrap metal used in foundries.

Recycling is very similar the rotting (decaying), and reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.

@@

Some of the scholar uses recycling \citep{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it.  Many scholar used the word recycling when mentioning works use trash and the concept of it. However they are not mentioning the meaning that is decomposing things to the their particles. What they is actually is reusing and combining things, concepts, creating new mixtures. It is hard to say that they use it wrongly, but what they refer is actually upcycling. Creative reuse, inventing new things from discard. Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to “the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life.” It is argued that art, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste. This theory counters the argument that an object is dead once it is disposed of \citep{emgin2012trashion}. Some of the scholars and artist uses upcycling for their process. This thesis project is about those objects that are recreated from trash through the process of upcycling.

% FROM Susan Strasser
% According to the Oxford English Dictionary, recycling originated in the oil industry during the 1920s, describing partially refined petroleum sent through the refining cycle again to reduce waste. Its use broadened during the 1960s, designating all kinds of reuse and reclamation, and the world became familiar during the early 1970s, as the burgeoning environmental movement promoted the separate collection of certain kinds of trash to promote their reuse in manufacturing.

% RUBBISH NEWSPAPER

% All these variety of words forms her research and rubbish newspaper.

% these all words commonly used to refer is a subject of Alice Bradshaw's thesis and work. She analyzes each word in her rubbish newspaper. Figure X shows newspaper cover photo.

% The Museum of Contemporary Rubbish continues a tradition of celebrating and reversing the status of low culture objects within the ‘high status’ gallery space. Bradshaw reflects on this connection between rubbish and contemporary artistic practice in the Rubbish newspaper which is given away to visitors at the show. A large body of research is disseminated and contextualised in this throwaway (often unwanted) medium of the free newspaper. The subject of rubbish is broken down into its taxonomic elements (eg detritus, rejects, litter), these sub-categories become collections in themselves, of theories and works that have now been transformed through the disposable nature of the newspaper as medium. The paper communicates this research in a way which reflects on the content: through quotations, references and Bradshaw’s charmingly simplistic renderings of the artworks she cites, each section is made up of remains. Here, Bradshaw has linked a review of discarded waste with contemporary practice, and, even further, she adapts Walter Benjamin’s method in the paper made up of quotations, and an exhibition consisting of elements found whilst wandering the urban space. Connecting the writer’s earlier comparison of the poet and rag picker, here the artist becomes the collector and hoarder of waste.

% Her works shows us that the increasing interests on the subject starting from the beginning of the 20th century.

% use it "brings to mind"

>>>>

According to dictionary Merriam-Webster, trash means anything useless, worthless or discarded. In parallel to this definition, the common perception is to get rid of them as soon as possible. People tend to think that trash is valueless because it is no longer needed or not wanted anymore. People want to get rid of them not thinking any alternative. Stav says that \quotes{[t]hey forget about it and don’t think about all the time and energy and money put into disposing of it} \citep[as cited in][]{navarro2015followingtrash}. On the other hand the issue of trash and transformation is not that simple. There are a lot of points to examine the trash.

% TODO Summarize
% Change in the production and consumption practices
\quotes{Over the course of the twentieth century, the twin developments of mass production and mass media in the capitalist economies of the Western Countries completed a total transformation of everyday life, reorienting almost every activity toward consumption. Things once locally produced and often handmade were now mass produced and commodified, turning local, artisanal producers into deskilled laborers serving the assembly line} \citep{pye2010trashculture}. As the result of it amount of goods boost and the cost of them significantly reduced. Things once reused again and again, now thrown away because it is more affordable to replace with new one. As the production increased its by-product material waste is also increased. \quotes{The phenomenon of waste comes clearly into focus not merely as a by-product of manufacturing processes, but rather as an integral element in cycles of production and consumption} \citep{pye2010trashculture}.

% Dominant approaches
During the last decades much attention has been devoted to the waste. In particularly environmental considerations dominates the perceptions of waste. \cite{ibarra2015beautiful} writes that \quotes{despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding}.

The act of trashing objects and the process of transforming them is not limited with geography, nationality and modern ages. It is a very common concept from developed cities to rural areas, from modern societies to ancient ones \citep[33]{rathje1992rubbish}. Anyone can encounter with trash in the crowded urban areas \quotes{as well as the remotest corners of the world} \citep[16]{cerny1996recycled}.

Trash is everywhere and, produced every time. It is inseparable from people's activities. \quotes{Every day, [people] put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from} \citep[xxv]{zimring2012encyclopedia} their habitat. In other words, refuse is part of people's daily activities. Production of it never stops. Various activities of life such as eating, drinking, working and traveling leave behind wastes. These activities are not only taking place every time, but also spread to different places such as homes, offices and picnic areas. It is hard to say that any place is waste free. Nearly every place require waste bin because people can easily access vary kinds of goods that are going to be thrown away after used. If people do not find a waste bin, they often leave their trash wherever possible.

Trash is in the streets, in people's home, in the sea that people swim, rotating around the globe \footnote{Satellite discards are disposed to the atmosphere and they rotate around the globe like satellites.}. Even if trash is tried to move away from people's habitat, it is as close as the nearest waste bin.

@@

The vast amount of discarded items spread through the landfills to oceans. As commodities spread to the every corner of the world, trash do also. It moves from homes to garbage trucks, from streets to landfills and also from landfills to sculptures inside museums. In other words, trash is not only found on the most disgusting and avoided places, but also can be found on the most steril and frequently visited places.

% Different scales
The scale of trash production is not same for everybody or every country. \cite[2]{chen2015waste} writes that: 
\begin{quote}
The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD\footnote{OECD (Organization for Economic Co-operation and Development) is an international economic organization of 34 countries. Turkey is a member of this organization.} countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.
\end{quote}

Similar to these as stated by \cite[16]{cerny1996recycled} \quotes{a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away.} Moreover from trash many unexpected results can be extracted. \cite[xxv]{zimring2012encyclopedia} argues that:
\begin{quote}
Our trash is a testament; what we throw away says much about our values, our habits, and our lives. ... Our trash is part of us, whether or not we choose to acknowledge it. ... The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream.
\end{quote}

% Different types
Electronic waste, construction and demolition waste, medical waste are some of the various types of waste. They are result of different production and consumption practices. For example nuclear power generation and applications of nuclear fission or nuclear technology produces not only engery but also radioactive waste which is very dangerous for living creatures.

% Different diciplines
Trash attracts the attention of different peoples and disciplines \quotes{ranging from economics to environmental studies, but most particularly by those studying consumerism or material culture} \citep[63]{emgin2012trashion}. For instance for archaeologist dumps near the residential area are one of the significant places to figure out what people consume in the ancient times \citep{rathje1992rubbish}. Moreover scholars argues that there is a relationship between technological and waste. Trash can be seen as a design and technological problem \citep{mcdonough2010cradle}. Further economical aspect of trash can not ignored. \cite[65]{emgin2012trashion} states that there is a huge business based on eco-friendly products and recyclable goods that is increasingly promoted.

% Different people
Various people including garbage collectors and artists interact with trash for different purposes. There are people who collects plastics, scraps and papers from waste bins and landfills. For the ragpickers, collecting others excess and discard is significant source of economical income. They collect and clasify recycle materials to sell them. By collecting and selling them they endure their life. On the other side for some of the people it is not considered as trash. As stated by the editor of the Garbage issue of ReVista, Christmas decorations at Chocó, a poor region on Colombia’s Pacific Coast, are \quotes{all crafted from used tin cans, old newspapers, discarded textiles and found wood objects} \citep{erlick2015editorsletter}. She realized that any of them called the practice as recycling. For them using trash again and again is very natural and it is part of their life. On the contrary for the developed countries trash considered as a thing that must be avoided. There is no place for trash in their life. It can be understood from this anectode that approaches to the garbage are not same for all regions of the world. It can be said that \quotes{perceptions of waste and the value of material are neither static nor universally shared} \citep[xxvi]{zimring2012encyclopedia}.

As noted by \cite{pye2010trashculture} \quotes{at least since the early twentieth century, the concern with discarded things and materials has been a recurring theme in art}. In the beginning of the 20th century objects that are considered as art enter the scope of art making. Using non-art objects in the art opened new dimensions for the language of art and practice art making. This is a revolutionary change in the practice of art making. Production of art and the approach to the art changed dramatically. Picasso and Baraque are the first artists that used non-art object in their works. Later many of artists such as Kurt Schwitters and Joseph Cornell followed them with their collages and assemblages. Later Duchamp challenged the nature of art by using, non-unique, fabricated object to express his ideas. His work changed the way of perceiving art dramatically. With these developments trash has found a place in the art and contemporary artists become interested in trash. They use trash for different purposes and these are explored in detail in the following chapters. Trash find places in many mediums such as sculptures, paintings, assemblages and photographs. Artist express themselves through trash. Portraits are build from trash. Consumption habits of society are criticized through trash. \cite[2]{pye2010trashculture} states that \quotes{trash have influenced, and are also influenced by, cultural products such as films, visual art, museum exhibits and literature}.

%****************************************
\section{Purpose of the Study}
As it can be seen clearly that there are different aspects and approaches to the trash. In this thesis study to understand them is a key element because main driving force is to explore the alternative perceptions of trash. It is not static, not fixed, not totally isolated from people and social life. Instead of creating new usages, combinations or alternatives, common approach is to ignore all the possibilities embedded to the trash. People often do not look beyond the primary function of objects. To establish a solid understanding of trash and transformation of it, we have to give more attention to the trash. In order to move away the common perception this study asks that is it possible to reuse discarded items rather than refusing them?

The aim of this study is to explore the theories and methods focused on transformation of trash in the context of art and artistic act. Particularly this thesis is interested in the relationship between art and waste. It investigates that how waste represented as a subject and how waste is used as an art material to represent or draw attention to the other subjects. It asks and seeks answers of these questions: Why and how is trash used by the artist? Are there any differences with the original (or untouched, or blank) items compared to discarded (or used) items? Has using discarded material or trash have specific (or special) meaning (or message)?

Thesis project focuses on disposable items and specifically paper trash. Its purpose is to transform trash and make it worth to reconsider. At this point I need to state that the process of transformation is not to be confused with the kind of industrial recycling that is applying automated procedures to the products such as paper cups, glass bottles, plastics caps and aluminum cans with the purpose of returning them to the industrial production as raw materials. Further many people are inside the business of transforming trash through recycling and reusing. People has been looking for aluminum cans, glass bottles and plastics on the streets. They collect and sell them to survive. There are companies that are collect waste materials to regain them to the industry. In thesis they are not in the scope. Artist that give attention to the trash and transform them is in the scope of this thesis.

% TODO relocation.
% MOVE TO Conclusion of art chapter, discussion of transformation.
% FROM Trashion: The Return of the Disposed by Bahar Emgin
%\ People are often eager to see objects that were once considered useless and tasteless when they have been invigorated with new life.

@@

%****************************************
\section{A Note on Terminology}
Many scholars and authors have used broad range of terms to refer the notion. Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter are some of them. Sometimes these words are used to signify same concept. Although there are slight differences between these words. This situation signifies that literature of trash is so wide and there is no consensus on terminology. Words are used interchangeably. The book Rubbish: the Archeology of Garbage gives clearer definition of some these words:

\begin{quote}
Several words for the things we throw away ---\quotes{garbage}, \quotes{trash}, \quotes{refuse}, \quotes{rubbish}--- are used synonymously in causal speech but in fact have different meanings. \textit{Trash} refers specifically to discards that are at least theoretically \quotes{dry} ---newspapers, boxes, cans, and so on. \textit{Garbage} refers technically to wet discards--- food remains, yard waste, and offal. Refuse is an inclusive term for both the wet discards and the dry. Rubbish is even more inclusive: It refers to all refuse plus construction and demolition debris. The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrelevant, but may see a revival if the idea of composting food and yard waste catches on. We will frequently use "garbage" in this book to refer to the totality of human discards because it is the word used naturally in ordinary speech. The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen. \citep[9]{rathje1992rubbish}
\end{quote}

Artist Alice Bradshaw has published a \quotes{Rubbish Newspaper} which contains these words and shows their place in litreature and artworks. It is based on her extensive researh on this subject.

In addition to these there is also a confusion of the terms: reuse and recycling which are the general methods of transforming trash to the another object or concept. Both of them are used widely by scholars.

According to dictionary Merriam-Webster, the word reuse means \quotes{to use again especially in a different way or after reclaiming or reprocessing.} Reusing involves usage of the same product unchanged in form. Reusing lengthens the life of the item or material. The main purpose is to make the item last as long as it can. To reuse is to use something again instead of throwing it away. In this thesis, reuse is explored through the work of the artist.

On the other hand recycle means \quotes{to treat or process (used or waste materials) so as to make suitable for reuse.} In recycling an item, it is processed into a totally new product. Recycling occurs when waste in an unchanged chemical form is used in the same process that created the original product. Crushed glass containers used to make new glass containers, and scrap metal used in foundries can ge given as examples.

Recycling is very similar the rotting, and reuse is something like dry tree branches used by birds for their nest. These are two agents of nature to regain their resources.

@@

\cite[72]{strasser1999waste} explains recycling by referring to the Oxford English Dictionary as:
\begin{quote}
... recycling originated in the oil industry during the 1920s, describing partially refined petroleum sent through the refining cycle again to reduce waste. Its use broadened during the 1960s, designating all kinds of reuse and reclamation, and the world became familiar during the early 1970s, as the burgeoning environmental movement promoted the separate collection of certain kinds of trash to promote their reuse in manufacturing.
\end{quote}

Some of the scholars use recycling \citep{cerny1996recycled,herman1998trashformations} for the recreation and transformation of waste. Many scholar used the word recycling when mentioning works use trash and the concept of it. However they are not mentioning the meaning that is decomposing things to the their particles. What they is actually is reusing and combining things, concepts, creating new mixtures. It is hard to say that they use it wrongly, but what they refer is actually upcycling. Creative reuse, inventing new things from discard. Upcycling is a term used by architect and designer William McDonaugh and chemist Michael Braungart and refers to \quotes{the process of converting an industrial nutrient (material) into something of similar or greater value, in its second life} \citep[as cited in][63]{emgin2012trashion}. It is argued that art, in this instance, acts as a tool of transformation and reintroduces into certain orders what was once deemed waste. This theory counters the argument that an object is dead once it is disposed of \citep{emgin2012trashion}. Some of the scholars and artist uses upcycling for their process. This thesis project is about those objects that are recreated from trash through the process of upcycling.
